### 2022-03-10 sections/bdt_Htautau.tex
update tables and plots

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
(a1) & (a2) & (a3) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
(b1) & (b2) & (b3) \\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
(c1) \\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit'). The uncertainty band includes both the statistical and systematic uncertainties in the background prediction. Overflow bins are included respectively in the last bin. Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) 
channels. 
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the ratios of the data to the background prediction.}
\label{fig:taupt_prefit}
\end{figure}

>>>>

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
(a1) & (a2) & (a3) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}\\
(b1) & (b2) \\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}\\
(c1) & (c2) \\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2) before the fit to data ('Pre-Fit'). The uncertainty band includes both the statistical and systematic uncertainties in the background prediction. Overflow bins are included respectively in the last bin. Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) 
channels. 
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the ratios of the data to the background prediction.}
\label{fig:taupt_prefit}
\end{figure}
